\chapter{English version of Völuspá verses}

Völuspá is the first and most known poem of the Poetic Edda.
It tells the story of the creation of the world and its coming end, Ragnarök.
It is told by a Völva, a seer so to speak, to Óðinn.

For the interested, I leave here the English translation of the verses scattered throughout the thesis.
The numbering of verses depends on the edition of the poem you will find, mine is from the textbook used in schools in Iceland.
The English translations are also in a different stanza, where two lines are combined as compared to the Icelandic versions.
The verses chosen, and where they are placed throughout the thesis, roughly represent the birth of the world, its demise and then eventual rebirth.

\textbf{3rd verse:}\\
``\emph{
Of old was the age | when Ymir lived; \\
Sea nor cool waves | nor sand there were; \\
Earth had not been, | nor heaven above, \\
But a yawning gap, | and grass nowhere. 
}'' \\
\textbf{6th verse:}\\
``\emph{
Then sought the gods | their assembly-seats, \\
The holy ones, | and council held; \\
Names then gave they | to noon and twilight, \\
Morning they named, | and the waning moon, \\
Night and evening, | the years to number.
}'' \\
\textbf{19th verse}\\
``\emph{
An ash I know, | Yggdrasil its name, \\
With water white | is the great tree wet; \\
Thence come the dews | that fall in the dales, \\
Green by Urth's well | does it ever grow.
}'' \\
\textbf{21st verse:}\\
``\emph{
The war I remember, | the first in the world, \\
When the gods with spears | had smitten Gullveig, \\
And in the hall | of Hár had burned her, \\
Three times burned, | and three times born, \\
Oft and again, | yet ever she lives.
i}'' \\
\textbf{28th verse:}\\
``\emph{
Alone I sat | when the Old One sought me, \\
The terror of gods, | and gazed in mine eyes: \\
``What hast thou to ask? | why comest thou hither? \\
Odin, I know | where thine eye is hidden.''\\
I know where Odin's | eye is hidden, \\
Deep in the wide-famed | well of Mimir; \\
Mead from the pledge | of Odin each mom \\
Does Mimir drink: | would you know yet more? 
}'' \\
\textbf{44th verse:}\\
``\emph{
Brothers shall fight | and fell each other, \\
And sisters' sons | shall kinship stain; \\
Hard is it on earth, | with mighty whoredom; \\
Axe-time, sword-time, | shields are sundered, \\
Wind-time, wolf-time, | ere the world falls; \\
Nor ever shall men | each other spare.
}'' \\
\textbf{55th verse:}\\
``\emph{
The sun turns black, | earth sinks in the sea, \\
The hot stars down | from heaven are whirled; \\
Fierce grows the steam | and the life-feeding flame, \\
Till fire leaps high | about heaven itself. 
}'' \\
\textbf{57th verse:}\\
``\emph{
Now do I see | the earth anew \\
Rise all green | from the waves again; \\
The cataracts fall, | and the eagle flies, \\
And fish he catches | beneath the cliffs.
}'' \\
\textbf{63rd verse:}\\
``\emph{
From below the dragon | dark comes forth, \\
Nidhogg flying | from Nidafjoll; \\
The bodies of men on | his wings he bears, \\
The serpent bright: | but now must I sink. 
}''
